---
title: "APM Analysis"
output: html_notebook
---

```{r echo=FALSE}
library(dplyr)
library(ggplot2)
library(caret)
```

```{r}
master_data <- read.csv('data/HDdata.csv')
```

### Preprocess Data
```{r}
# Split out the dependent variable
heart_data <- master_data[, 1:10]
y <- master_data[,11]

# Split out training and test data
training_indexes <- createDataPartition(y, p=.70, list = F)
X_train <- heart_data[training_indexes, 1:10]
y_train <- y[training_indexes]
X_test <- heart_data[-training_indexes, 1:10]
y_test <- y[-training_indexes]
```

### Initial Analysis
In your data are there:
	a. NAs?
	Yes, there are 10 NAs in the age column. All other columns do not have any NA values.
	
	b. categorical values?
	No, there are no categorical values/variables. Some columns could have been categorical,   but they have already been encoded numerically.
	
	c. binary values?
	Yes, the sex, fbs, and exang variables contain binary values.
	
	d. numeric (real number) values?
  Yes, all columns contain numberic values. Furthermore, all columns are type integer       except for the oldpeak variable which is type double. 




